---
title       : Car Mileage Presentation
subtitle    : Analysis of ggplot's mpg data
author      : mikeg
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Introduction

This presentation analyzes the **mpg** dataset in *ggplot2's* package to determine cars with the best and worst average mile per gallon. The average mile per gallon for each car is determined by taking the mean of its highway and city mile per gallon.

--- .class #id 



## Best Mileage
```{r}
require(ggplot2)

# select key columns from dataset
df <- subset(mpg, select = c(manufacturer,model,year,class))
df$mpg <- (mpg$hwy + mpg$cty)/2

# sort data in descending order based on mpg
df <- with(df, df[order(mpg, decreasing=TRUE),])
# display top 5 cars with best miles per gallon
head(df, n=5)
```


---

## Worst Mileage
```{r}

# display bottom 5 cars with worst miles per gallon
tail(df, n=5)
```

---

## Summary
1. Volkswagen makes cars with highest average miles per gallon (mpg)
2. Dodge and Jeep make cars with lowest average miles per gallon (mpg)
3. On average, compact and subcompact cars have better mpg than trucks and pickups

